MT @HanBaldwin: Fightin OOVs in German \#twitter

### 2013-07-30 darmstadt_gscl_2013/article_twitter_normalization.tex
small update of related work

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{makeidx}  % allows for indexgeneration
\usepackage{paralist} % for inparaenum
\usepackage{multirow} % for multirow
\usepackage{tabularx} % for centering in table
\usepackage{url}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\totaloov}{\% of total OOVs}
\newcommand{\uniqoov}{\% of unique OOVs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\pagestyle{headings}  % switches on printing of running heads
\title{MT @HanBaldwin: Fightin OOVs in German \#twitter}
\titlerunning{Makn Sens a Germa \#twitter}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Uladzimir Sidarenka \and Tatjana Schef\/f\/ler \and Manfred Stede}
%
\authorrunning{Sidarenka et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Uladzimir Sidarenka, Tatjana Schef\/f\/ler, Manfred Stede}
%
\institute{University of Potsdam,\\
  \email{{uladzimir.sidarenka@uni-potsdam.de,
      tatjana.scheffler@uni-potsdam.de,
      manfred.stede@uni-potsdam.de},\\ WWW home page:
    \texttt{http://www.ling.uni-potsdam.de/acl-lab/SocMedia/main.htm}}}

@@

  This article gives an overview of existing approaches to the problem
  of out-of-vocabulary (OOV) tokens and noisiness phenomena in natural
  language texts. These approaches are classified with regard to the
  size of text spans and knowledge inference mechanisms which they
  rely on in their work. Subsequently, quantitative and qualitative
  analyses of unknown words are conducted on German Twitter messages,
  in order to show how relevant the OOV and text normalization
  problems are for this particular kind of micro-texts and what their
  characteristics are there. In a concluding step, we present a set of
  ad-hoc techniques which are supposed to tackle some of the most
  prominent disturbing effects found during the analyses and show how
  this set of techniques helps us to lower the average rate of
  out-of-vocabulary tokens in Twitter messages thereby improving the
  quality of their automatic Part-of-speech tagging.

@@

Starting from the second half of the 1990s, not only the number of
publications on automatic text correction gradually increased every
year but also the focus of those researches steadily turned away from
normalization of manually typed or OCR processed official documents to
the processing of sloppily created user messages and online chat
posts. But even despite this increased interest, most of the
researches still were dealing with only English text data. A few
exceptions from that are works on French (Beaufort et al.,
\cite{beaufort}) and Spanish (Oliva et al., \cite{oliva}).

@@

In this article we are going to provide some more insight about the
relevance of OOV issues for German language by showing how many
out-of-vocabulary tokens are found in German online texts on average
and what kind of linguistic phenomena are main sources of these
OOVs. The next Section will first give a short overview and provide a
classification of recent scientific approaches to the problem of
out-of-vocabulary words in non-standard texts. After that, in Section
\ref{error:analysis} we will analyze which types of noisiness
phenomena are especially common in German Twitter. Section
\ref{normalization} will subsequently describe an automatic procedure
for mitigating some of the most prominent of those effects. In a
concluding step, we will perform an evaluation of the results of this
procedure and give some further suggestions for future research.

@@

Before proceeding with the description of existing methods for noisy
text normalization (NTN), we first would like to define the criteria
by which these methods could be classified. It should be noted that
there already exist several classifications of NTN approaches
including, for example, Kukich (\cite{kukich}), Kobus et
al. (\cite{kobus}), and Sproat et al. (\cite{sproat}). But all of
these classifications seem to share one significant common
shortcoming, namely they try to involve several independent criteria
within one classification scheme.

Kukich (\cite{kukich}), for example, divided NTN techniques into six
classes:
\begin{enumerate}
\item minimum edit distance techniques;
\item similarity key techniques;
\item rule-based techniques;
\item \textit{n}-gram based techniques;
\item probabilistic techniques;
\item neural nets.
\end{enumerate}

Kobus (\cite{kobus}), on the contrary, referred to NTN methods as
\textit{metaphors} and split them into the following three groups:
\begin{enumerate}
\item ``spell checking'' metaphor;
\item ``translation'' metaphor;
\item ``speech recognition'' metaphor.
\end{enumerate}

Though both divisions seem to be justified to some extent, it is
difficult to determine using them whether an NTN approach that detects
and restores incorrectly spelled words on the basis of phonetical
\textit{n}-gram statistics should fall into the \textit{n}-gram based,
probabilistic, spell checking or speech recognition class.

Instead of that, we suggest using two separate types of criteria which
are unrelated to each other and characterize NTN approaches from
different points of view.

The first criterion is \emph{segmentation level}. It primarily depends
on the maximal length of syntagmatic segments which are used
\begin{inparaenum}[\itshape a\upshape)]
\item to infer in-vocabulary (IV) equivalents for OOV
  tokens\label{candidate:inferring} and
\item to choose the most probable variant\label{candidate:selection}
  among multiple possible suggestions\footnote{For the cases, when
    segments of different lengths are used for tasks
    \ref{candidate:inferring} and \ref{candidate:selection}, we note
    it explicitly in our classification on which segmentation length
    each of these subtasks relies.}.
\end{inparaenum} For this criterion we propose division into the following
classes:
\begin{enumerate}
  \item graphematic\footnote{Depending on whether phonetical
    information is involved or not at this level, this class could be
    further divided into a phonographematic and purely graphematic
    subclasses.};
  \item lexical;
  \item phrasal.
\end{enumerate}
Each broader level of this hierarchy is also supposed to either
incorporate or ignore information provided by its narrower
subsegments. In this way, only one (the broadest) hierarchical class
needs to be mentioned for the cases when multiple segmentation levels
are involved by some techniques.

The second classification criterion regards the \emph{type of
  information induction} that is used to devise the correction
directives. This leads us to the usual NLP-taxonomy which divides all
approaches into:
\begin{enumerate}
  \item rule-based;
  \item statistical\footnote{Depending on the type of training data
    required, this class is in turn usually divided into unsupervised,
    semi-supervised, and supervised groups.};
  \item and hybrid ones.
\end{enumerate}

Equipped with these two criteria, it should now be easier to get a
clear picture of the development and recent tendencies in NTN
research.

It is worthwile noting that many approaches to NTN, especially the
earlier ones, were heavily influenced by the idea of noisy channel
model. The underlying notion of this model was that observed sentences
had to be considered as corrupted versions of their respective
original language signals. In order to restore the undistorted signal,
one had to come up with two probabilistic submodels: the error model
(one which caused the corruption) and the language model (one which
reflected the nature of initial signal source). To these works belong
Brill and Moore (\cite{brill}), Sproat et al. (\cite{sproat}),
Toutanova and Moore (\cite{toutanova}), Clark
(\cite{alexander-clark}), Choudhury et al. (\cite{choudhury}), Cook
and Stevenson (\cite{cook}), Beaufort et al. (\cite{beaufort})
etc. The majority of these methods used either purely graphematic
(Brill and Moore, \cite{brill}; Sproat et al., \cite{sproat}; Clark,
\cite{alexander-clark}) or phonographematic segmentation (Toutanova
and Moore \cite{toutanova}; Choudhury et al., \cite{choudhury}; Cook
and Stevenson, \cite{cook}) for error models. For language model,
normally phrasal segments (word \textit{n}-grams) were used. From the
point of view of information induction almost all of these techniques
could be characterized as supervised statistical, with the exception
of Cook and Stevenson (\cite{cook}) who claimed to use an unsupervised
technique.

The raising influence and improved quality of machine translation
tools and applications in the 2000s lead to the development of NTN
technologies which used broader levels of segmentation. In \cite{aw},
Aw et al. suggested a supervised statistical system for normalization
of SMS-messages. Their system operated exclusively on phrasal level. A
few years later, Clark and Araki (\cite{clark-araki}) described a
purely rule-based phrasal technique.

As stated by Kobus et al. (\cite{kobus}), NTN methods relying on
either graphematic or phrasal segments usually revealed complementary
strengths and weaknesses. This notion led NLP scientists to the idea
that incorporating multiple levels of language in one NTN system could
improve the total quality of the system as a whole since different
levels would benefit from each other. As a consequence of this notion,
a wealth of combined techniques emerged in the past few years. Among
these we should especially mention Kobus et al. (\cite{kobus}),
Kaufmann (\cite{kaufmann}), Han and Baldwin (\cite{han}), and Oliva et
al. (\cite{oliva}). The system suggested by Kobus et
al. (\cite{kobus}), for example, used a hybrid phrasal approach in a
pre-processing step and subsequently fed the output of this
pre-processing into a finite state transducer (FST). The FST performed
a phonographematic segmentation of data and derived normalization
equivalents on the basis of statistical inference. Another approach
proposed by Kaufmann (\cite{kaufmann}) first used unambigous lexical
mappings and straightforward graphematic correction rules to reduce
the noisiness effects and then redirected pre-normalized input to a
statistical phrasal MT system.

Eventually, in \cite{han}, an article called ``Lexical Normalization
of Short Text Messages: Makn Sens a \#{}twitter'' was published by Han
and Baldwin. In this article the authors separated the tasks of
identification of ill-formed words and finding appropriate correction
for them. For the former problem, they first generated a confusion set
(CS) for each word unknown to \texttt{GNU aspell}. Based on this set,
the decision was made whether a particular word had to be corrected or
regarded as vlid. Subsequently, for words identified as ill-formed the
most probable restoration candidate was chosen from CS by combining
features resulting from dictionary lookup, analysis of surrounding
context, and estimating word similarity to each proposed correction
variant. According to authors' estimations, this combination allowed
them to outperform most of the NTN methods existing at that time.

In the next Section will also perform quantitive and qualitative
analyses of unknown words in German Twitter texts in order to assess
whether and to what extent the problem of ill-formed words is relevant
for them. Relying on these analyses we then will suggest a set of
ad-hoc techniques which could help one lower the average rate of
incorrectly spelled words in this kind of text.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{makeidx}  % allows for indexgeneration
\usepackage{paralist} % for inparaenum
\usepackage{multirow} % for multirow
\usepackage{tabularx} % for centering in table
\usepackage{url}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\totaloov}{\% of total OOVs}
\newcommand{\uniqoov}{\% of unique OOVs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\pagestyle{headings}  % switches on printing of running heads
\title{MT @HanBaldwin: Fightin OOVs in German \#twitter}
\titlerunning{Makn Sens a Germa \#twitter}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Uladzimir Sidarenka \and Tatjana Scheffler \and Manfred Stede}
%
\authorrunning{Sidarenka et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Uladzimir Sidarenka, Tatjana Scheffler, Manfred Stede}
%
\institute{University of Potsdam,\\
  \email{{uladzimir.sidarenka@uni-potsdam.de,
      tatjana.scheffler@uni-potsdam.de,
      manfred.stede@uni-potsdam.de},\\ WWW home page:
    \texttt{http://www.ling.uni-potsdam.de/acl-lab/SocMedia/main.htm}}}

@@

  This article gives an overview of existing approaches to the problem
  of out-of-vocabulary (OOV) tokens and noisiness phenomena in natural
  language texts. These approaches are classified with regard to the
  size of text spans and knowledge inference mechanisms which they
  rely on in their work. Additionally to that, we conduct quantitative
  and qualitative analyses of unknown words in German Twitter
  messages, in order to see how relevant the OOV and text
  normalization problems are for this particular kind of micro-texts
  and what the characteristics of these OOVs are. In a concluding
  step, we present a set of ad-hoc techniques which are supposed to
  tackle some of the most prominent disturbing effects found during
  these analyses and show how this set of techniques helps us lower
  the average rate of out-of-vocabulary tokens in Twitter messages and
  how this lower OOV-rate helps improve the quality of automatic
  Part-of-speech tagging.

@@

%% Starting from the second half of the 1990s, not only the number of
%% publications on automatic text correction gradually increased every
%% year but also the focus of those researches steadily turned away from
%% normalization of manually typed or OCR processed official documents to
%% the processing of sloppily created user messages and online chat
%% posts. But even despite this increased interest, most of the
%% researches still were dealing with only English text data. A few
%% exceptions from that are works on French (Beaufort et al.,
%% \cite{beaufort}) and Spanish (Oliva et al., \cite{oliva}).

@@

%% In this article we are going to provide some more insight about the
%% relevance of OOV issues for German language by showing how many
%% out-of-vocabulary tokens are found in German online texts on average
%% and what kind of linguistic phenomena are main sources of these
%% OOVs. The next Section will first give a short overview and provide a
%% classification of recent scientific approaches to the problem of
%% out-of-vocabulary words in non-standard texts. After that, in Section
%% \ref{error:analysis} we will analyze which types of noisiness
%% phenomena are especially common in German Twitter. Section
%% \ref{normalization} will subsequently describe an automatic procedure
%% for mitigating some of the most prominent of those effects. In a
%% concluding step, we will perform an evaluation of the results of this
%% procedure and give some further suggestions for future research.

In the next Section we will give a short overview of recent scientific
approaches to the problem of tackling out-of-vocabulary words in
non-standard texts. After that, in Section \ref{error:analysis} we
will analyze which types of noisiness phenomena are especially
characteristic for German Twitter. Section \ref{normalization} will
subsequently describe an automatic procedure for mitigating some of
the most prominent of those effects. In a concluding step, we will
perform an evaluation of the results of this procedure and give
further suggestions for future research.

@@

Before proceeding with the description of existing methods for noisy
text normalization (NTN), we first would like to define the criteria
by which these methods could be classified. It should be noted that
there already exist several classifications of NTN approaches
including Kukich (\cite{kukich}), Kobus et al. (\cite{kobus}), and
Sproat et al. (\cite{sproat}).
%% But all of these classifications seem to share one significant common
%% shortcoming, namely they try to involve several independent criteria
%% within one classification scheme.

So, Kukich (\cite{kukich}), for example, divided NTN techniques into
six classes:
\begin{enumerate}
\item minimum edit distance techniques;
\item similarity key techniques;
\item rule-based techniques;
\item \textit{n}-gram based techniques;
\item probabilistic techniques;
\item neural nets.
\end{enumerate}
Kobus (\cite{kobus}), on the contrary, referred to NTN methods as
\textit{metaphors} and split them into the following three groups:
\begin{enumerate}
\item ``spell checking'' metaphor;
\item ``translation'' metaphor;
\item ``speech recognition'' metaphor.
\end{enumerate}

Though both divisions seem to be justified to some extent, it is
difficult to determine using them whether an NTN approach that detects
and restores incorrectly spelled words on the basis of phonetical
\textit{n}-gram statistics should fall into \textit{n}-gram based,
probabilistic, spell checking or speech recognition class.

The reason for this confusion is the fact that the above
classifications both rely on several independent criteria at the same
time though each of these criteria characterizes an NTN system from a
different point of view. As a consequence, unambiguous assignment of
an NTN approach to one particular class often becomes impossible. In
order to avoid this, we instead suggest using separate classifications
for each criterion without mixing them.

One of such criteria which in our opinion would be worth a separate
classification is \emph{segmentation level} which is used
\begin{inparaenum}[\itshape a\upshape)]
\item to infer in-vocabulary (IV) equivalents for OOV
  tokens\label{candidate:inferring} and
\item to choose the most probable variant\label{candidate:selection}
  among multiple possible ones\footnote{For the cases, when segments
    of different lengths are used for tasks \ref{candidate:inferring}
    and \ref{candidate:selection}, we note it explicitly in our
    classification on which segmentation length each of these subtasks
    relies.}.
\end{inparaenum} For this criterion, we propose division into the following
classes:
\begin{enumerate}
  \item graphematic\footnote{Depending on whether phonetical
    information is involved or not at this level, this class could be
    further divided into a phonographematic and purely graphematic
    subclasses.};
  \item lexical;
  \item phrasal.
\end{enumerate}
Each broader level of this hierarchy is also supposed to either
incorporate or ignore information provided by its narrower
subsegments. In this way, we only need to mention one (the broadest)
hierarchical class for the cases when multiple segmentation levels are
involved by some techniques.

The second criterion regards the \emph{type of information induction}
that is used to devise the correction rules. This leads us to the
usual NLP-taxonomy which divides all approaches into:
\begin{enumerate}
  \item rule-based;
  \item statistical\footnote{Depending on the type of training data
    required, this class is in turn usually divided into unsupervised,
    semi-supervised, and supervised groups.};
  \item and hybrid ones.
\end{enumerate}

With these two classifications, we will now try to present and group
together approaches to the NTN task which appeared in the literature
in recent years.

The earlier works on NTN commonly used either purely graphematic or
phonographematic levels of segmentation for deriving normalization
variants of incorrectly spelled words. To purely graphematic systems
belong methods suggested Brill and Moore (\cite{brill}), Sproat et
al. (\cite{sproat}), and Clark (\cite{alexander-clark}). As
phonographematic approaches one could regard works done by Toutanova
and Moore (\cite{toutanova}), Choudhury et al. (\cite{choudhury}),
Cook and Stevenson (\cite{cook}) etc. With regard to the type of
information inference, practically all of these methods were
supervised with the exception of Cook and Stevenson (\cite{cook}) who
claimed to uns an unsupervised technique.

Starting from the second half of the 2000s, the raising influence and
improved quality of machine translation tools lead to the development
of NTN technologies which used broader levels of segmentation. In
\cite{aw}, Aw et al. suggested a supervised statistical system for
normalization of SMS-messages which operated on automatically aligned
phrases. A few years later, Clark and Araki (\cite{clark-araki})
described a purely rule-based method which used mappings of
non-standard words and phrases to their corresponding standard
language forms.

As noted by Kobus et al. (\cite{kobus}), NTN methods relying on either
graphematic or phrasal segments usually revealed complementary
strengths and weaknesses. This notion led NLP scientists to the idea
that by incorporating multiple levels of the language into one NTN
system the total performace of the system would improve as different
sources of information would benefit from each other. As a consequence
of this, a wealth of combined techniques emerged in the past few
years. Among these we should especially mention the works by Kobus et
al. (\cite{kobus}), Kaufmann (\cite{kaufmann}), Han and Baldwin
(\cite{han}), and Oliva et al. (\cite{oliva}). These systems used the
whole range of segmentation levels from phonographematatic to the
phrasal one, and also different knowledge inference techniques were
applied for different levels.

%% Eventually, in \cite{han}, an article called ``Lexical Normalization
%% of Short Text Messages: Makn Sens a \#{}twitter'' was published by Han
%% and Baldwin. In this article the authors separated the tasks of
%% identification of ill-formed words and finding appropriate correction
%% for them. For the former problem, they first generated a confusion set
%% (CS) for each word unknown to \texttt{GNU aspell}. Based on this set,
%% the decision was made whether a particular word had to be corrected or
%% regarded as vlid. Subsequently, for words identified as ill-formed the
%% most probable restoration candidate was chosen from CS by combining
%% features resulting from dictionary lookup, analysis of surrounding
%% context, and estimating word similarity to each proposed correction
%% variant. According to authors' estimations, this combination allowed
%% them to outperform most of the NTN methods existing at that time.

It should however be noted that almost all of the above methods mainly
concentrated on only English text data. A few exceptions from that are
works done by Beaufort et al. (\cite{beaufort}) for French and Oliva
et al. (\cite{oliva}) for Spanish. To find out which peculiarities of
ill-formed words are characteristic for German, we will perform a
quantitive and qualitative analysis of unknown words in German Twitter
in the next Section to see what kind of NTN techniques would be more
suitable for handling ill-formed words there.
